\documentclass[10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[version=4]{mhchem}
\usepackage{stmaryrd}

\begin{document}
\section*{Math 494 \\
 Practice problem set 1}
\newpage
Problem 1. Show that if \(K\) is a field and \(R \neq\{0\}\) is a ring, then every ring homomorphism \(K \rightarrow R\) is injective.

\newpage
Problem 2. Let \(R\) be a finite commutative ring.\\
i) Prove that every prime ideal of \(R\) is a maximal.\\
ii) Deduce that if \(R\) is reduced, then \(R\) is (isomorphic to) a finite product of fields.

\newpage
Problem 3. Let \(R=\mathbf{Z}[x]\).\\
i) Show that the ideal \((2, x)\) is a maximal ideal.\\
ii) Is the ideal ( \(2, x^{2}\) ) maximal? prime? radical?

\newpage
Problem 4. Let \(f: \mathbf{Z} \rightarrow \mathbf{Z} / 6 \mathbf{Z} \times \mathbf{Z} / 4 \mathbf{Z}\) be given by \(f(u)=(u+6 \mathbf{Z}, u+4 \mathbf{Z})\).\\
i) Is \(f\) a ring homomorphism?\\
ii) Is \(f\) surjective?

\newpage
Problem 5. Let \(S\) be a commutative ring and \(R=S[x, y] /\left(x^{2}, x y\right)\). Show that \(R /(\bar{x})\) is isomorphic to \(S[y]\).

\newpage
Problem 6. Let \(I\) and \(J\) be ideals in a commutative ring \(R\).\\
i) Show that \(\operatorname{rad}(I J)=\operatorname{rad}(I \cap J)=\operatorname{rad}(I) \cap \operatorname{rad}(J)\).\\
ii) Give an example where \(I J \neq I \cap J\).

\newpage
Problem 7. Let \(R_{1}\) and \(R_{2}\) be commutative rings and \(R=R_{1} \times R_{2}\).\\
i) Show that if \(P_{1}\) is a prime ideal in \(R_{1}\) and \(P_{2}\) is a prime ideal in \(R_{2}\), then \(P_{1} \times R_{2}\) and \(R_{1} \times P_{2}\) are prime ideals in \(R\).\\
ii) Show that every ideal \(P\) in \(R\) is of one of the types described in i).

\newpage
Problem 8. Prove or disprove the following assertions:\\
i) If \(I\) and \(J\) are ideals in a commutative ring \(R\) such that \(R / I \simeq R / J\), then \(I=J\).\\
ii) If \(S\) is a multiplicative system in a commutative ring \(R\) and \(S^{-1} R\) is a field, then every element of \(S\) is a non-zero-divisor.\\
iii) If \(I \subseteq J\) are ideals in a commutative ring \(R\) and \(R / I\) is Noetherian, then \(R / J\) is Noetherian.

\newpage
Problem 9. Let \(d \in \mathbf{Z}\) which is not a square. Show that the ring \(\mathbf{Z}[\sqrt{d}]\) is Noetherian.

\newpage
Problem 10. Show that the rings \(\mathbf{Z}[\sqrt{2}]\) and \(\mathbf{Z}[\sqrt{3}]\) are not isomorphic.


\end{document}